```{r}
install.packages("e1071")
install.packages("ROCR")
install.packages("glmnet")

library(e1071)
library(ROCR)
library(tidyverse)
library(tidymodels)
library(readr)
library(dplyr)
library(glmnet)
parole <- read_csv("~/Desktop/Grad  School /BAN 502/parole.csv")

```
```{r}
parole = parole %>% mutate(male = as_factor(male)) %>% 
  mutate(male = fct_recode(male, "female" = "0", "male" = "1" )) 

parole = parole %>% mutate(race = as_factor(race)) %>% 
  mutate(race = fct_recode(race, "otherwise" = "2", "white" = "1" )) 

parole = parole %>% mutate(state = as_factor(state)) %>% 
  mutate(state = fct_recode(state, "Kentucky" = "2", "Louisiana" = "3", "Virginia" = "4", "other state" = "1")) 

parole = parole %>% mutate(crime = as_factor(crime)) %>% 
  mutate(crime = fct_recode(crime, "larceny" = "2", "drug-related" = "3", "driving-related" = "4", "other crime" = "1")) 

parole = parole %>% mutate(multiple.offenses = as_factor(multiple.offenses)) %>% 
  mutate(multiple.offenses = fct_recode(multiple.offenses, "otherwise" = "0", "multiple offenses" = "1")) 

parole = parole %>% mutate(violator = as_factor(violator)) %>% 
  mutate(violator = fct_recode(violator, "completed parole" = "0", "violated parole" = "1")) 
```

```{r}
summary(parole)
```

```{r}
set.seed(12345) 
parole_split = initial_split(parole, prop = 0.70, strata = violator)
train = training(parole_split)
test = testing(parole_split)

levels(train$violator)

train = train %>% mutate(violator = fct_relevel(violator, c("No", "Yes")))
levels(train$violator)
```

```{r}
parole_model = 
  logistic_reg(mode = "classification") %>% 
  set_engine("glm") 

parole_recipe = recipe(violator ~ state, train)

logreg_wf = workflow() %>%
  add_recipe(parole_recipe) %>% 
  add_model(parole_model)

parole_fit = fit(logreg_wf, train)
```

```{r}
summary(parole_fit$fit$fit$fit)
```


```{r}
parole_model2 = 
  logistic_reg(mode = "classification") %>% 
  set_engine("glm") 

parole_recipe2 = recipe(violator ~ state + multiple.offenses + race, train)

logreg_wf = workflow() %>%
  add_recipe(parole_recipe2) %>% 
  add_model(parole_model2)

parole_fit2 = fit(logreg_wf, train)
```

```{r}
summary(parole_fit2$fit$fit$fit)
```

```{r}
newdata = data.frame(state = "Louisiana", multiple.offenses = "multiple offenses", race = "white")
predict(parole_fit2, newdata, type="prob")
```


```{r}
predictions = predict(parole_fit2, train, type="prob") 
head(predictions)
```
```{r}
predictions = predict(parole_fit2, train, type="prob")[2]
head(predictions)
```

```{r}
ROCRpred = prediction(predictions, train$violator) 
ROCRperf = performance(ROCRpred, "tpr", "fpr")
plot(ROCRperf, colorize=TRUE, print.cutoffs.at=seq(0,1,by=0.1), text.adj=c(-0.2,1.7))
```

```{r}
as.numeric(performance(ROCRpred, "auc")@y.values)
```

```{r}
opt.cut = function(perf, pred){
    cut.ind = mapply(FUN=function(x, y, p){
        d = (x - 0)^2 + (y-1)^2
        ind = which(d == min(d))
        c(sensitivity = y[[ind]], specificity = 1-x[[ind]], 
            cutoff = p[[ind]])
    }, perf@x.values, perf@y.values, pred@cutoffs)
}
print(opt.cut(ROCRperf, ROCRpred))
```

```{r}
t1 = table(train$violator,predictions > 0.2015788)
t1
```
```{r}
(t1[1,1]+t1[2,2])/nrow(train)
```

```{r}
#sensitivity 
36/(18+36)

```

### Question 14 
```

```{r}
predictions2 = predict(parole_fit2, test, type="prob") 
head(predictions2)
```
```{r}
predictions2 = predict(parole_fit2, test, type="prob")[2]
head(predictions2)
```


```{r}
ROCRpred_2 = prediction(predictions2, test$violator) 
ROCRperf_2 = performance(ROCRpred, "tpr", "fpr")
plot(ROCRperf, colorize=TRUE, print.cutoffs.at=seq(0,1,by=0.1), text.adj=c(-0.2,1.7))
```
```{r}
opt.cut = function(perf, pred){
    cut.ind = mapply(FUN=function(x, y, p){
        d = (x - 0)^2 + (y-1)^2
        ind = which(d == min(d))
        c(sensitivity = y[[ind]], specificity = 1-x[[ind]], 
            cutoff = p[[ind]])
    }, perf@x.values, perf@y.values, pred@cutoffs)
}
print(opt.cut(ROCRperf, ROCRpred))
```
```{r}
t2 = table(test$violator,predictions2 > 0.05)
t2
(t2[1,1]+t1[2,2])/nrow(test)
```
```{r}
t2 = table(test$violator,predictions > 0.05)
t2
```

